Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-08 thesis/chapters/ch_chapter1.tex
Final edits to fit with thesis style

\chapter[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
\let\thefootnote\relax\footnotetext{This section contains text from an article published in \cite{Emerick2019}}

@@

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In \cite{Emerick2018b} we investigate the importance of ionizing radiation in regulating star formation and driving outflows in our galaxy. In \cite{Emerick2018c} we explore how individual metal species mix within the ISM and are ejected via galactic winds.

@@

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance. However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.

@@

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we investigate this in detail in \cite{Emerick2018c}.

@@

\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This is explored in more detail in \citep{Emerick2018c}.
\end{enumerate}

@@

%\clearpage
%\appendix

\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}

@@

\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

>>>>

\chapter[Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars ]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
\let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2019}}

@@

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In \cite{Emerick2018b} we investigate the importance of ionizing radiation in regulating star formation and driving outflows in our galaxy. In \cite{Emerick2018b} we explore how individual metal species mix within the ISM and are ejected via galactic winds.

@@

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance. However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HQM2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.

@@

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we investigate this in detail in \cite{Emerick2018b}.

@@

\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This is explored in more detail in \citep{Emerick2018b}.
\end{enumerate}

@@

%\clearpage
%\appendix
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

@@
